Dewlap color variation in \textit{Anolis sagrei} is maintained between habitats within islands of the West Indies

### 2020-07-04 ms/sections/discussion.tex
implemented colin's comments and refactored the discussion to put more emphasis on neutral processes

\paragraph{Dewlap coloration differs between habitat-types} We found that male dewlap coloration in \textit{A. sagrei} significantly varied between habitat-types (beach scrub bush, primary coppice forest and mangrove forest) on five islands of the West Indies: Abaco, Bimini, Cayman Brac, Little Cayman and Long Island. However, the habitat-specific variation in dewlaps was not consistent between these islands. Although those results are consistent with adaptation at a very local scale, other evolutionary drivers could be at work, including phenotypic plasticity, random drift, or historical contingency, including multiple colonization events. We reject this last explanation because all of the island populations in this study are strictly monophyletic, implying a single colonization event per island (van de Schoot, unpublished thesis; \citealt{Driessens2017, Reynolds2020}). While random drift cannot be completely ruled out, we see little evidence for a role of phenotypic isolation-by-distance (spatial autocorrelation) in explaining the differences we report. We did detect a significant signal of isolation-by-distance on Eleuthera, but we did not find differences in dewlap coloration between habitats on this island.

% The maintenance of divergence in the face of gene flow

\paragraph{Divergence is maintained in the face of gene flow} We detected differences between habitats at relatively small spatial scales, most of the time between sites 5-10km apart, and sometimes a few hundred meters away. This, together with the lack of geographic barriers within islands and the high mobility of \textit{A. sagrei} individuals \citep{Kamath2018}, imply ample opportunity for extensive gene flow between our study populations. In agreement with this, populations from different habitats were found to not be monophyletic based on <insert marker name here> (van de Schoot et al. unpublished thesis). The maintenance of phenotypic differences at such a small spatial scales, in the face of gene flow, may support an adaptive explanation \citep{Richardson2014}.\\

The persistence of dewlap color divergence despite gene flow has been documented in multiple species of anoles, sometimes in relation to environmental conditions. \citet{Ng2012} and \citet{Ng2016} found divergent dewlap coloration in the face of gene flow between subspecies of \textit{A. distichus} across Hispaniola, and proposed this as a mechanism of reproductive isolation in the early stages of speciation \citep{Ng2011, Lambert2013, Ng2017}. \citet{Stapley2011} found that dewlap color polymorphism was maintained in the absence of genetic structure between populations of \textit{A. apletophallus} from Panama. \citet{Thorpe2002a} found that divergence in dewlap coloration matched habitat-type better than mitochondrial lineage in \textit{A. roquet} on Martinique, and a convergent pattern was found in \textit{A. trinitatis} on the featureless island of St Vincent \citep{Thorpe2002b}. Finally, divergence in body coloration, but not dewlap coloration, was also reported in \textit{A. conspersus} on another small island, Grand Cayman \citep{Macedonia2001}. Altogether, our results align with previous studies suggesting a generally high adaptive potential of dewlap coloration in anoles over small distances, which could apply to \textit{A. sagrei}.

% Could there be local adaptation? To what?

\paragraph{Dewlap coloration could be locally adapted} Presently, we do not know the adaptive drivers of dewlap color divergence observed in this study. Some degree of parallel evolution is usually a good indicator for an adaptive process \citep{Losos2011}, and convergent patterns of dewlap color evolution in similar environments across islands and species have been documented in other species \citep{Thorpe2002a, Thorpe2002b}. Here, however, we found little consistency in between-habitat divergence across the nine islands studied; except maybe for dewlap brightness being lower in the primary coppice habitat on three islands, and the primary coppice habitat being intermediate in coloration between mangrove and beach scrub on two islands. Those patterns could reflect adaptation to components of the habitat \citep{Endler1988}, but it is not clear what those components of the habitat might be. Although those patterns could reflect adaptation to components of the habitat \citep{Endler1988}, it is not clear what those components might be. Alternatively, neutral processes could produce patterns similar to local adaptation, such that this possibility cannot be completely ruled out \citep{Miles2019} (full subsection for this?).\\

Previous studies have suggested that dewlap coloration may have evolved to be maximally detectable under local light conditions imposed by the environment, primarily through UV contrast (i.e. UV-brighter dewlaps in UV-dark, mesic habitats and UV-darker dewlaps in UV-bright, xeric habitats), in \textit{A. cristatellus} and \textit{A. cooki} from Puerto Rico \citep{Leal2002, Leal2004}. Although UV reflectance was commonly involved in between-habitat divergence, we found no such patterns in \textit{A. sagrei}, where instead, we found the darkest dewlaps in the darkest, mesic habitat -- primary coppice forest -- on three islands, and dewlaps often differed the most between beach scrub and mangrove forest, two xeric habitats with similar, high irradiance levels \citep{Howard1950, Schoener1968}. The inconsistent and idiosyncratic patterns we observed suggest that dewlap color variation between habitats cannot be predicted by habitat identity alone. Studies of Jamaican and Hispaniolan anoles similarly found between-habitat differences in dewlap coloration but no evidence for higher detectability \citep{Fleishman2009, Ng2012}. Habitats on different islands may also differ in other aspects than light conditions such as densities of predators or other anole species, which have been shown to affect among-island dewlap diversity \citep{Vanhooydonck2009, Baeckens2018}. In particular, \citet{Baeckens2018} recently showed that dewlaps with spotted patterns occurred more often in \textit{A. sagrei} on islands with more coexisting species of anoles. Therefore, dewlap coloration in $A. sagrei$ may be under the influence of a mosaic of interacting local environmental factors, which need not be the same across islands.

>>>>

\paragraph{Dewlap coloration differs between habitat-types} We found that male dewlap coloration in \textit{A. sagrei} significantly varied between habitat-types (beach scrub bush, primary coppice forest and mangrove forest) on five islands of the West Indies: Abaco, Bimini, Cayman Brac, Little Cayman and Long Island. However, the habitat-specific variation in dewlaps was not consistent between these islands. Although those results are consistent with adaptation at a very local scale, other evolutionary drivers could be at work, including phenotypic plasticity, random drift, or historical contingency, including multiple colonization events. We reject this last explanation because all of the island populations in this study are strictly monophyletic, implying a single colonization event per island (van de Schoot, unpublished thesis; \citealt{Driessens2017, Reynolds2020}).

\paragraph{A role of neutral drift is unlikely} Differences in organismal traits between environments are not necessarily proof of adaptation or selection, and genetic drift may result in patterns similar to local adaptation \citep{Miles2019}. Nevertheless, two lines of evidence from our data suggest that this scenario may be implausible. First, we found little evidence for a role of phenotypic isolation-by-distance (spatial autocorrelation) in explaining the differences we report. We did detect a significant signal of isolation-by-distance on Eleuthera, but there were no differences in dewlap coloration between habitats on this island. Second, we detected differences between habitats at relatively small spatial scales, most of the time between sites 5-10km apart, sometimes a few hundred meters away, on Bimini for example. Such small-scale differences would be unlikely under strong gene flow \citep{Richardson2014}. Our study islands lack geographic barriers to the movement of $A. sagrei$, which have been shown to be highly mobile on these islands \citep{Kamath2018}, implying widespread gene flow across sites and habitats. Moreover, habitat-populations were found to be non-monophyletic with respect to <insert marker name here> (van de Schoot et al. unpublished thesis), which is also suggestive of gene flow.\\

Our results align with previous documented cases of persistence of dewlap color divergence despite gene flow in multiple species of anoles, sometimes in relation to environmental conditions. \citet{Ng2012} and \citet{Ng2016} found divergent dewlap coloration in the face of gene flow between subspecies of \textit{A. distichus} across Hispaniola, and proposed this as a mechanism of reproductive isolation in the early stages of speciation \citep{Ng2011, Lambert2013, Ng2017}. \citet{Stapley2011} found that dewlap color polymorphism was maintained in the absence of genetic structure between populations of \textit{A. apletophallus} from Panama. \citet{Thorpe2002a} found that divergence in dewlap coloration matched habitat-type better than mitochondrial lineage in \textit{A. roquet} on Martinique, and a convergent pattern was found in \textit{A. trinitatis} on the featureless island of St Vincent \citep{Thorpe2002b}. Finally, divergence in body coloration, but not dewlap coloration, was also reported in \textit{A. conspersus} on another small island, Grand Cayman \citep{Macedonia2001}.\\

\paragraph{Dewlap coloration could be locally adapted} Although phenotypic divergence at small spatial scales may be an indicator of local adaptation, the inconsistency of the between-habitat divergence patterns we observed across islands implies that neutral processes cannot be definitely ruled out \citep{Losos2011}. Conversely, the absence of parallel divergence across islands does not rule out local adaptation either \citep{Losos2011}. If selection has an effect, it may be dependent on aspects of the environment that are not encompassed by our broad habitat-type classification into coastal dry scrub, primary coppice forest and mangrove forest, and dewlap coloration may be influenced by a mosaic of interacting local environmental factors, which need not be the same across islands.\\

Previous studies have described convergent patterns of dewlap color evolution in similar environments across islands and species \citep{Thorpe2002a, Thorpe2002b}. Others have suggested that dewlap coloration may have evolved to be maximally detectable under local light conditions imposed by the environment, primarily through UV contrast (i.e. UV-brighter dewlaps in UV-dark, mesic habitats and UV-darker dewlaps in UV-bright, xeric habitats), in \textit{A. cristatellus} and \textit{A. cooki} from Puerto Rico \citep{Leal2002, Leal2004}. Although UV reflectance was commonly involved in between-habitat divergence, we found no such patterns in \textit{A. sagrei}, where instead, we found the darkest dewlaps in the darkest, mesic habitat -- primary coppice forest -- on three islands, and dewlaps often differed the most between beach scrub and mangrove forest, two xeric habitats with similar, high irradiance levels \citep{Howard1950, Schoener1968}. The inconsistent and idiosyncratic patterns we observed suggest that dewlap color variation between habitats cannot be predicted by habitat identity alone. Studies of Jamaican and Hispaniolan anoles similarly found between-habitat differences in dewlap coloration but no evidence for higher detectability \citep{Fleishman2009, Ng2012}. Habitats on different islands may also differ in other aspects than light conditions such as densities of predators or other anole species, which have been shown to affect among-island dewlap diversity \citep{Vanhooydonck2009, Baeckens2018}. In particular, \citet{Baeckens2018} recently showed that dewlaps with spotted patterns occurred more often in \textit{A. sagrei} on islands with more coexisting species of anoles. Therefore, dewlap coloration in $A. sagrei$ may be under the influence of a mosaic of interacting local environmental factors, which need not be the same across islands.

### 2020-07-04 ms/sections/suppfigures.tex
implemented colin's comments and refactored the discussion to put more emphasis on neutral processes

% Map of each island
\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{../maps/detailed_map.pdf}
	\caption{Map of the sampling sites and corresponding habitats across nine islands of the West Indies.}
	\label{supfig:map}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/03-PCA/figure_brightness"}
	\caption{Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score for each island. Pearson's squared correlation coefficients are reported. *, P < 0.05.}	
	\label{supfig:brightness}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{"../analyses/03-PCA/figure_brightness_pooled"}
	\caption{Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score across the whole archipelago. Pearson's squared correlation coefficient is reported. *, P < 0.05.}
	\label{supfig:brightness_pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth]{"../analyses/06-pooled/figure_pooled"}
	\caption{(A) Principal component scores and 5\% confidence ellipses across habitats for the whole archipelago. The principal component analysis was performed on reflectance data from all islands pooled together. (B) PCA rotation matrix showing the loadings of each wavelength from 300 to 700nm onto the principal components.}
	\label{supfig:pooled}
\end{figure}

% Reflectance curves
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/02-reflectance/figure_reflectance"}
	\caption{5-95th percentile range of lizard dewlap reflectance values (in \% of incoming light) across wavelengths for each island and each habitat.}
	\label{supfig:reflectance}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/classif_svm_pca_pooled"}
	\caption{Archipelago-wide SVM classification accuracy based on principal component data. Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/classif_svm_refl_pooled"}
	\caption{Archipelago-wide SVM classification accuracy based on reflectance data at 50nm-intervals in wavelength (see Methods). Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{"../analyses/04-machine learning/plots/importance_svm_pca_pooled"}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on principal component data (Figure \ref{supfig:classif-svm-pca-pooled}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{"../analyses/04-machine learning/plots/importance_svm_refl_pooled"}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on reflectance data at 50nm-intervals in wavelength (Figure \ref{supfig:classif-svm-refl-pooled}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/classif_lda_pca_pooled"}
	\caption{Archipelago-wide LDA classification accuracy based on principal component data. Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/classif_lda_refl_pooled"}
	\caption{Archipelago-wide LDA classification accuracy based on reflectance data at 50nm-intervals in wavelength (see Methods). Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{"../analyses/04-machine learning/plots/classif_lda_pca"}
	\caption{LDA classification accuracy across islands based on principal component data. Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{"../analyses/04-machine learning/plots/classif_svm_refl"}
	\caption{SVM classification accuracy across islands based on reflectance data at 50nm-intervals in wavelength (see Methods). Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{"../analyses/04-machine learning/plots/classif_lda_refl"}
	\caption{LDA classification accuracy across islands based on reflectance data at 50nm-intervals in wavelength (see Methods). Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/importance_svm_pca"}
	\caption{Sensitivity analyses of the different input variables in the within-island SVM classification on principal component data (Figure \ref{supfig:classif-svm-pca}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/importance_lda_pca"}
	\caption{Sensitivity analyses of the different input variables in the within-island LDA classification on principal component data (Figure \ref{supfig:classif-lda-pca}), with relative importance computed for every machine.}
	\label{supfig:importance-lda-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/importance_svm_pca"}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on reflectance at 50nm-intervals in wavelength (Figure \ref{supfig:classif-svm-refl}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{"../analyses/04-machine learning/plots/importance_lda_pca"}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide LDA classification on reflectance at 50nm-intervals in wavelength (Figure \ref{supfig:classif-lda-refl}), with relative importance computed for every machine.}
	\label{supfig:importance-lda-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{"../analyses/10-distances/figure_distances2"}
	\caption{Spatial scale of between-habitat differences in dewlap coloration. For each variable and each pair of habitats where significant differences were detected (Figure \ref{fig:anova}), we performed multiple post hoc pairwise comparisons between the sites involved (Figure \ref{supfig:map}, Table \ref{suptab:sites}), using nonparametric Wilcoxon-Mann-Whitney tests. Here we report, for each pair of habitats, the distances between sites that significantly differed in dewlap coloration at an error rate of 0.05 (P-values corrected with the Benjamini-Hochberg procedure for multiple testing).}
	\label{supfig:distances}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{"../analyses/09-parallelism/figure_contrasts"}
	\caption{Test of parallel divergence between islands. Differences in habitat-means, or contrasts, are shown for two pairs of habitats for each principal component on each island, rescaled so the standard deviation of the means along each principal component is one. The contrasts represent the patterns of between-habtiat variation on each island, for a given principal component. The absence of clustering of islands by variable indicates that islands differ in their between-habitat divergence patterns. This is confirmed by a non-significant MANOVA test of the between versus within-variable variance in contrasts.}
	\label{supfig:contrasts}
\end{figure}

>>>>

% Map of each island
\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{suppfigures/detailed_map.pdf}
	\caption{Map of the sampling sites and corresponding habitats across nine islands of the West Indies.}
	\label{supfig:map}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/figure_brightness.png}
	\caption{Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score for each island. Pearson's squared correlation coefficients are reported. *, P < 0.05.}	
	\label{supfig:brightness}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{suppfigures/figure_brightness_pooled.png}
	\caption{Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score across the whole archipelago. Pearson's squared correlation coefficient is reported. *, P < 0.05.}
	\label{supfig:brightness_pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth]{suppfigures/figure_pooled.png}
	\caption{(A) Principal component scores and 5\% confidence ellipses across habitats for the whole archipelago. The principal component analysis was performed on reflectance data from all islands pooled together. (B) PCA rotation matrix showing the loadings of each wavelength from 300 to 700nm onto the principal components.}
	\label{supfig:pooled}
\end{figure}

% Reflectance curves
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/figure_reflectance.png}
	\caption{5-95th percentile range of lizard dewlap reflectance values (in \% of incoming light) across wavelengths for each island and each habitat.}
	\label{supfig:reflectance}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/classif_svm_pca_pooled.png}
	\caption{Archipelago-wide SVM classification accuracy based on principal component data. Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/classif_svm_refl_pooled.png}
	\caption{Archipelago-wide SVM classification accuracy based on reflectance data at 50nm-intervals in wavelength (see Methods). Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{suppfigures/importance_svm_pca_pooled.png}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on principal component data (Figure \ref{supfig:classif-svm-pca-pooled}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{suppfigures/importance_svm_refl_pooled.png}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on reflectance data at 50nm-intervals in wavelength (Figure \ref{supfig:classif-svm-refl-pooled}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/classif_lda_pca_pooled.png}
	\caption{Archipelago-wide LDA classification accuracy based on principal component data. Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-pca-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/classif_lda_refl_pooled.png}
	\caption{Archipelago-wide LDA classification accuracy based on reflectance data at 50nm-intervals in wavelength (see Methods). Machines were trained on individual dewlaps regardless of island identity. The histogram shows the accuracy distribution over 100 replicates for each five cross-validation bins. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-refl-pooled}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{suppfigures/classif_lda_pca.png}
	\caption{LDA classification accuracy across islands based on principal component data. Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{suppfigures/classif_svm_refl.png}
	\caption{SVM classification accuracy across islands based on reflectance data at 50nm-intervals in wavelength (see Methods). Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-svm-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{suppfigures/classif_lda_refl.png}
	\caption{LDA classification accuracy across islands based on reflectance data at 50nm-intervals in wavelength (see Methods). Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The legend is the same as in Figure \ref{fig:classif-svm-pca}.}
	\label{supfig:classif-lda-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/importance_svm_pca.png}
	\caption{Sensitivity analyses of the different input variables in the within-island SVM classification on principal component data (Figure \ref{supfig:classif-svm-pca}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/importance_lda_pca.png}
	\caption{Sensitivity analyses of the different input variables in the within-island LDA classification on principal component data (Figure \ref{supfig:classif-lda-pca}), with relative importance computed for every machine.}
	\label{supfig:importance-lda-pca}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/importance_svm_pca.png}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide SVM classification on reflectance at 50nm-intervals in wavelength (Figure \ref{supfig:classif-svm-refl}), with relative importance computed for every machine.}
	\label{supfig:importance-svm-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{suppfigures/importance_lda_pca.png}
	\caption{Sensitivity analyses of the different input variables in the archipelago-wide LDA classification on reflectance at 50nm-intervals in wavelength (Figure \ref{supfig:classif-lda-refl}), with relative importance computed for every machine.}
	\label{supfig:importance-lda-refl}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{suppfigures/figure_distances2.png}
	\caption{Spatial scale of between-habitat differences in dewlap coloration. For each variable and each pair of habitats where significant differences were detected (Figure \ref{fig:anova}), we performed multiple post hoc pairwise comparisons between the sites involved (Figure \ref{supfig:map}, Table \ref{suptab:sites}), using nonparametric Wilcoxon-Mann-Whitney tests. Here we report, for each pair of habitats, the distances between sites that significantly differed in dewlap coloration at an error rate of 0.05 (P-values corrected with the Benjamini-Hochberg procedure for multiple testing).}
	\label{supfig:distances}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{suppfigures/figure_contrasts.png}
	\caption{Test of parallel divergence between islands. Differences in habitat-means, or contrasts, are shown for two pairs of habitats for each principal component on each island, rescaled so the standard deviation of the means along each principal component is one. The contrasts represent the patterns of between-habtiat variation on each island, for a given principal component. The absence of clustering of islands by variable indicates that islands differ in their between-habitat divergence patterns. This is confirmed by a non-significant MANOVA test of the between versus within-variable variance in contrasts.}
	\label{supfig:contrasts}
\end{figure}
